Fourmile Calibrations and Output

### 2025-01-26 fourmile_output_dec2024.Rmd
added rest of cals and forward runs in for dec2024 model edits

# grid_2011 <- read_cals(grid_2011., name = 'grid_2011')
# grid_2012 <- read_cals(grid_2012., name = 'grid_2012')
# grid_2013 <- read_cals(grid_2013., name = 'grid_2013')
# grid_2014 <- read_cals(grid_2014., name = 'grid_2014')
# grid_2015 <- read_cals(grid_2015., name = 'grid_2015')
# grid_2016 <- read_cals(grid_2016., name = 'grid_2016')
# grid_2017 <- read_cals(grid_2017., name = 'grid_2017')
# grid_2018 <- read_cals(grid_2018., name = 'grid_2018')
# grid_2019 <- read_cals(grid_2019., name = 'grid_2019')
# grid_2020 <- read_cals(grid_2020., name = 'grid_2020')
grid_all <- read_cals(grid_all.c, name = 'grid_all')

# grid <- bind_rows(grid_2011, grid_2012, grid_2013, grid_2014, grid_2015,
#                   grid_2016, grid_2017, grid_2018, grid_2019, grid_2020,
#                   grid_all) %>%
#   mutate(input_data = 'grid') %>%
#   mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
#   dplyr::select(-c(year_missing_almost)) %>%
#   rename(param = Parameter) %>%
#   filter(!param == 'locGrw',
#          !param == 'tempRes')

grid <- grid_all %>%
  mutate(input_data = 'grid') %>%
  mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost)) %>%
  rename(param = Parameter) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes')

# statn_2011 <- read_cals(statn_2011, name = 'statn_2011')
# statn_2012 <- read_cals(statn_2012, name = 'statn_2012')
# statn_2013 <- read_cals(statn_2013, name = 'statn_2013')
# statn_2014 <- read_cals(statn_2014, name = 'statn_2014')
# statn_2015 <- read_cals(statn_2015, name = 'statn_2015')
# statn_2016 <- read_cals(statn_2016, name = 'statn_2016')
# statn_2017 <- read_cals(statn_2017, name = 'statn_2017')
# statn_2018 <- read_cals(statn_2018, name = 'statn_2018')
# statn_2019 <- read_cals(statn_2019, name = 'statn_2019')
# statn_2020 <- read_cals(statn_2020, name = 'statn_2020')
statn_all <- read_cals(statn_all., name = 'statn_all')

# statn <- bind_rows(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
#                   statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
#                   statn_all) %>%
#   mutate(input_data = 'statn') %>%
#   mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
#   dplyr::select(-c(year_missing_almost)) %>%
#   rename(param = Parameter) %>%
#   filter(!param == 'locGrw',
#          !param == 'tempRes')

statn <- statn_all %>%
  mutate(input_data = 'statn') %>%
  mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost)) %>%
  rename(param = Parameter) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes')

@@

# grid_2011_burn <- read_cals_burn(grid_2011., name = 'grid_2011')
# grid_2012_burn <- read_cals_burn(grid_2012., name = 'grid_2012')
# grid_2013_burn <- read_cals_burn(grid_2013., name = 'grid_2013')
# grid_2014_burn <- read_cals_burn(grid_2014., name = 'grid_2014')
# grid_2015_burn <- read_cals_burn(grid_2015., name = 'grid_2015')
# grid_2016_burn <- read_cals_burn(grid_2016., name = 'grid_2016')
# grid_2017_burn <- read_cals_burn(grid_2017., name = 'grid_2017')
# grid_2018_burn <- read_cals_burn(grid_2018., name = 'grid_2018')
# grid_2019_burn <- read_cals_burn(grid_2019., name = 'grid_2019')
# grid_2020_burn <- read_cals_burn(grid_2020., name = 'grid_2020')
grid_all_burn <- read_cals_burn(grid_all.c, name = 'grid_all')

# grid_burn <- bind_rows(grid_2011_burn, 
#                   grid_2012_burn, 
#                   grid_2013_burn, 
#                   grid_2014_burn, 
#                   grid_2015_burn,
#                   grid_2016_burn, 
#                   grid_2017_burn, 
#                   grid_2018_burn, 
#                   grid_2019_burn, 
#                   grid_2020_burn,
#                   grid_all_burn) %>%
#   mutate(input_data = 'grid') %>%
#   mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
#   dplyr::select(-c(year_missing_almost))

grid_burn <- grid_all_burn %>%
  mutate(input_data = 'grid') %>%
  mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost))

# now do statn burn params
# statn_2011_burn <- read_cals_burn(statn_2011, name = 'statn_2011')
# statn_2012_burn <- read_cals_burn(statn_2012, name = 'statn_2012')
# statn_2013_burn <- read_cals_burn(statn_2013, name = 'statn_2013')
# statn_2014_burn <- read_cals_burn(statn_2014, name = 'statn_2014')
# statn_2015_burn <- read_cals_burn(statn_2015, name = 'statn_2015')
# statn_2016_burn <- read_cals_burn(statn_2016, name = 'statn_2016')
# statn_2017_burn <- read_cals_burn(statn_2017, name = 'statn_2017')
# statn_2018_burn <- read_cals_burn(statn_2018, name = 'statn_2018')
# statn_2019_burn <- read_cals_burn(statn_2019, name = 'statn_2019')
# statn_2020_burn <- read_cals_burn(statn_2020, name = 'statn_2020')
statn_all_burn <- read_cals_burn(statn_all., name = 'statn_all')

# statn_burn <- bind_rows(statn_2011_burn, 
#                   statn_2012_burn, 
#                   statn_2013_burn, 
#                   statn_2014_burn, 
#                   statn_2015_burn,
#                   statn_2016_burn, 
#                   statn_2017_burn, 
#                   statn_2018_burn, 
#                   statn_2019_burn, 
#                   statn_2020_burn,
#                   statn_all_burn) %>%
#   mutate(input_data = 'statn') %>%
#   mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
#   dplyr::select(-c(year_missing_almost))

statn_burn <- statn_all_burn %>%
  mutate(input_data = 'statn') %>%
  mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost))

@@

# ggplot(params_combo, aes(x=burn, y=value, fill=input_data)) +
#   geom_boxplot() +
#   facet_wrap(~param, scales = 'free_y')
# 
# write_csv(params_combo, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/params_burn_unburn.csv')

@@

q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line() +
  scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            # "grid_2011"="seagreen",
                                            # "grid_2012"="seagreen2",
                                            # "grid_2013"="steelblue",
                                            # "grid_2014"='dodgerblue',
                                            # "grid_2015" = "cyan3",
                                            # 'grid_2016' = 'blue',
                                            # 'grid_2017' = 'blue4',
                                            # 'grid_2018' = 'cadetblue',
                                            # 'grid_2019' = 'lightgreen',
                                            # 'grid_2020' = 'olivedrab',
                                            'grid_all' = 'steelblue3',
                                            # "statn_2011"="maroon",
                                            # "statn_2012"="deeppink4",
                                            # "statn_2013"="deeppink",
                                            # "statn_2014"='purple',
                                            # "statn_2015" = "mediumorchid1",
                                            # 'statn_2016' = 'indianred',
                                            # 'statn_2017' = 'sienna',
                                            # 'statn_2018' = 'salmon2',
                                            # 'statn_2019' = 'mediumpurple1',
                                            # 'statn_2020' = 'violetred',
                                            'statn_all' = 'red')) +
  theme_bw(base_size=20)

@@

#plot annual cumulative Q vals for ensembles
plot_cumulq_yr_ <- function(calyear) {
  {flow_cumq %>%
    filter(year == calyear) %>%
    ggplot(aes(x = date,
               y = cumsum,
               color = cal_run)) +
    geom_line() +
scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            # "grid_2011"="seagreen",
                                            # "grid_2012"="seagreen2",
                                            # "grid_2013"="steelblue",
                                            # "grid_2014"='dodgerblue',
                                            # "grid_2015" = "cyan3",
                                            # 'grid_2016' = 'blue',
                                            # 'grid_2017' = 'blue4',
                                            # 'grid_2018' = 'cadetblue',
                                            # 'grid_2019' = 'lightgreen',
                                            # 'grid_2020' = 'olivedrab',
                                            'grid_all' = 'steelblue3',
                                            # "statn_2011"="maroon",
                                            # "statn_2012"="deeppink4",
                                            # "statn_2013"="deeppink",
                                            # "statn_2014"='purple',
                                            # "statn_2015" = "mediumorchid1",
                                            # 'statn_2016' = 'indianred',
                                            # 'statn_2017' = 'sienna',
                                            # 'statn_2018' = 'salmon2',
                                            # 'statn_2019' = 'mediumpurple1',
                                            # 'statn_2020' = 'violetred',
                                            'statn_all' = 'red')) +
    ggtitle(calyear) +
    theme_bw() +
    labs(y = 'Volume (m^3)')} %>%
    ggplotly()
}

@@

# flow_kge_all <- flow %>%
#   summarize(grid2011 = KGE(grid_2011, obs),
#             grid2012 = KGE(grid_2012, obs),
#             grid2013 = KGE(grid_2013, obs),
#             grid2014 = KGE(grid_2014, obs),
#             grid2015 = KGE(grid_2015, obs),
#             grid2016 = KGE(grid_2016, obs),
#             grid2017 = KGE(grid_2017, obs),
#             grid2018 = KGE(grid_2018, obs),
#             grid2019 = KGE(grid_2019, obs),
#             grid2020 = KGE(grid_2020, obs),
#             gridall = KGE(grid_all, obs),
#             statn2011 = KGE(statn_2011, obs),
#             statn2012 = KGE(statn_2012, obs),
#             statn2013 = KGE(statn_2013, obs),
#             statn2014 = KGE(statn_2014, obs),
#             statn2015 = KGE(statn_2015, obs),
#             statn2016 = KGE(statn_2016, obs),
#             statn2017 = KGE(statn_2017, obs),
#             statn2018 = KGE(statn_2018, obs),
#             statn2019 = KGE(statn_2019, obs),
#             statn2020 = KGE(statn_2020, obs),
#             statnall = KGE(statn_all, obs)) %>%
#     mutate_if(is.numeric,
#             round,
#             digits = 2)

flow_kge_all <- flow %>%
  summarize(
            gridall = KGE(grid_all,
                          obs, 
                          na.rm=T, 
                          method='2012'),
            statnall = KGE(statn_all, 
                           obs, 
                           na.rm=T,
                           method='2012')) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

@@

flow_year <- flow %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(
    # grid2011 = KGE(grid_2011, obs),
    #         grid2012 = KGE(grid_2012, obs),
    #         grid2013 = KGE(grid_2013, obs),
    #         grid2014 = KGE(grid_2014, obs),
    #         grid2015 = KGE(grid_2015, obs),
    #         grid2016 = KGE(grid_2016, obs),
    #         grid2017 = KGE(grid_2017, obs),
    #         grid2018 = KGE(grid_2018, obs),
    #         grid2019 = KGE(grid_2019, obs),
    #         grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs, na.rm = T, method='2012'),
            # statn2011 = KGE(statn_2011, obs),
            # statn2012 = KGE(statn_2012, obs),
            # statn2013 = KGE(statn_2013, obs),
            # statn2014 = KGE(statn_2014, obs),
            # statn2015 = KGE(statn_2015, obs),
            # statn2016 = KGE(statn_2016, obs),
            # statn2017 = KGE(statn_2017, obs),
            # statn2018 = KGE(statn_2018, obs),
            # statn2019 = KGE(statn_2019, obs),
            # statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs, na.rm=T, method='2012')) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

@@

<!-- ### Annual KGE plots -->

<!-- ```{r wy plots, echo = FALSE, message = FALSE, warning = FALSE} -->

<!-- plot_kge <- function(calyear) { -->
<!--   flow_plot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = model_run, -->
<!--                y = kge)) + -->
<!--     geom_point(size=3) + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
<!-- } -->

<!-- name <- levels(flow_plot$year) -->

<!-- lapply(name, plot_kge) -->

<!-- ``` -->

@@

flow_pbias_all <- flow %>%
  summarize(
    # grid2011 = pbias(grid_2011, obs),
    #         grid2012 = pbias(grid_2012, obs),
    #         grid2013 = pbias(grid_2013, obs),
    #         grid2014 = pbias(grid_2014, obs),
    #         grid2015 = pbias(grid_2015, obs),
    #         grid2016 = pbias(grid_2016, obs),
    #         grid2017 = pbias(grid_2017, obs),
    #         grid2018 = pbias(grid_2018, obs),
    #         grid2019 = pbias(grid_2019, obs),
    #         grid2020 = pbias(grid_2020, obs),
            gridall = pbias(grid_all, obs),
            # statn2011 = pbias(statn_2011, obs),
            # statn2012 = pbias(statn_2012, obs),
            # statn2013 = pbias(statn_2013, obs),
            # statn2014 = pbias(statn_2014, obs),
            # statn2015 = pbias(statn_2015, obs),
            # statn2016 = pbias(statn_2016, obs),
            # statn2017 = pbias(statn_2017, obs),
            # statn2018 = pbias(statn_2018, obs),
            # statn2019 = pbias(statn_2019, obs),
            # statn2020 = pbias(statn_2020, obs),
            statnall = pbias(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

@@

flow_year <- flow %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(
    # grid2011 = pbias(grid_2011, obs),
    #         grid2012 = pbias(grid_2012, obs),
    #         grid2013 = pbias(grid_2013, obs),
    #         grid2014 = pbias(grid_2014, obs),
    #         grid2015 = pbias(grid_2015, obs),
    #         grid2016 = pbias(grid_2016, obs),
    #         grid2017 = pbias(grid_2017, obs),
    #         grid2018 = pbias(grid_2018, obs),
    #         grid2019 = pbias(grid_2019, obs),
    #         grid2020 = pbias(grid_2020, obs),
            gridall = pbias(grid_all, obs),
            # statn2011 = pbias(statn_2011, obs),
            # statn2012 = pbias(statn_2012, obs),
            # statn2013 = pbias(statn_2013, obs),
            # statn2014 = pbias(statn_2014, obs),
            # statn2015 = pbias(statn_2015, obs),
            # statn2016 = pbias(statn_2016, obs),
            # statn2017 = pbias(statn_2017, obs),
            # statn2018 = pbias(statn_2018, obs),
            # statn2019 = pbias(statn_2019, obs),
            # statn2020 = pbias(statn_2020, obs),
            statnall = pbias(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

@@

<!-- ### Annual Pbias plots -->

<!-- ```{r pbias plots, echo = FALSE, message = FALSE, warning = FALSE} -->

<!-- plot_pbias <- function(calyear) { -->
<!--   flow_plot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = model_run, -->
<!--                y = pbias)) + -->
<!--     geom_point(size=3) + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
<!-- } -->

<!-- name <- levels(flow_plot$year) -->

<!-- lapply(name, plot_pbias) -->

<!-- ``` -->

>>>>

grid_2011 <- read_cals(grid_2011., name = 'grid_2011')
grid_2012 <- read_cals(grid_2012., name = 'grid_2012')
grid_2013 <- read_cals(grid_2013., name = 'grid_2013')
grid_2014 <- read_cals(grid_2014., name = 'grid_2014')
grid_2015 <- read_cals(grid_2015., name = 'grid_2015')
grid_2016 <- read_cals(grid_2016., name = 'grid_2016')
grid_2017 <- read_cals(grid_2017., name = 'grid_2017')
grid_2018 <- read_cals(grid_2018., name = 'grid_2018')
grid_2019 <- read_cals(grid_2019., name = 'grid_2019')
grid_2020 <- read_cals(grid_2020., name = 'grid_2020')
grid_all <- read_cals(grid_all.c, name = 'grid_all')

grid <- bind_rows(grid_2011, grid_2012, grid_2013, grid_2014, grid_2015,
                  grid_2016, grid_2017, grid_2018, grid_2019, grid_2020,
                  grid_all) %>%
  mutate(input_data = 'grid') %>%
  mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost)) %>%
  rename(param = Parameter) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes')

statn_2011 <- read_cals(statn_2011, name = 'statn_2011')
statn_2012 <- read_cals(statn_2012, name = 'statn_2012')
statn_2013 <- read_cals(statn_2013, name = 'statn_2013')
statn_2014 <- read_cals(statn_2014, name = 'statn_2014')
statn_2015 <- read_cals(statn_2015, name = 'statn_2015')
statn_2016 <- read_cals(statn_2016, name = 'statn_2016')
statn_2017 <- read_cals(statn_2017, name = 'statn_2017')
statn_2018 <- read_cals(statn_2018, name = 'statn_2018')
statn_2019 <- read_cals(statn_2019, name = 'statn_2019')
statn_2020 <- read_cals(statn_2020, name = 'statn_2020')
statn_all <- read_cals(statn_all., name = 'statn_all')

statn <- bind_rows(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
                  statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
                  statn_all) %>%
  mutate(input_data = 'statn') %>%
  mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost)) %>%
  rename(param = Parameter) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes')

@@

grid_2011_burn <- read_cals_burn(grid_2011., name = 'grid_2011')
grid_2012_burn <- read_cals_burn(grid_2012., name = 'grid_2012')
grid_2013_burn <- read_cals_burn(grid_2013., name = 'grid_2013')
grid_2014_burn <- read_cals_burn(grid_2014., name = 'grid_2014')
grid_2015_burn <- read_cals_burn(grid_2015., name = 'grid_2015')
grid_2016_burn <- read_cals_burn(grid_2016., name = 'grid_2016')
grid_2017_burn <- read_cals_burn(grid_2017., name = 'grid_2017')
grid_2018_burn <- read_cals_burn(grid_2018., name = 'grid_2018')
grid_2019_burn <- read_cals_burn(grid_2019., name = 'grid_2019')
grid_2020_burn <- read_cals_burn(grid_2020., name = 'grid_2020')
grid_all_burn <- read_cals_burn(grid_all.c, name = 'grid_all')

grid_burn <- bind_rows(grid_2011_burn,
                  grid_2012_burn,
                  grid_2013_burn,
                  grid_2014_burn,
                  grid_2015_burn,
                  grid_2016_burn,
                  grid_2017_burn,
                  grid_2018_burn,
                  grid_2019_burn,
                  grid_2020_burn,
                  grid_all_burn) %>%
  mutate(input_data = 'grid') %>%
  mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost))

# now do statn burn params
statn_2011_burn <- read_cals_burn(statn_2011, name = 'statn_2011')
statn_2012_burn <- read_cals_burn(statn_2012, name = 'statn_2012')
statn_2013_burn <- read_cals_burn(statn_2013, name = 'statn_2013')
statn_2014_burn <- read_cals_burn(statn_2014, name = 'statn_2014')
statn_2015_burn <- read_cals_burn(statn_2015, name = 'statn_2015')
statn_2016_burn <- read_cals_burn(statn_2016, name = 'statn_2016')
statn_2017_burn <- read_cals_burn(statn_2017, name = 'statn_2017')
statn_2018_burn <- read_cals_burn(statn_2018, name = 'statn_2018')
statn_2019_burn <- read_cals_burn(statn_2019, name = 'statn_2019')
statn_2020_burn <- read_cals_burn(statn_2020, name = 'statn_2020')
statn_all_burn <- read_cals_burn(statn_all., name = 'statn_all')

statn_burn <- bind_rows(statn_2011_burn,
                  statn_2012_burn,
                  statn_2013_burn,
                  statn_2014_burn,
                  statn_2015_burn,
                  statn_2016_burn,
                  statn_2017_burn,
                  statn_2018_burn,
                  statn_2019_burn,
                  statn_2020_burn,
                  statn_all_burn) %>%
  mutate(input_data = 'statn') %>%
  mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost))

@@

ggplot(params_combo, aes(x=burn, y=value, fill=input_data)) +
  geom_boxplot() +
  facet_wrap(~param, scales = 'free_y')
# 
# write_csv(params_combo, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/params_burn_unburn.csv')

@@

q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line() +
  scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            "grid_2011"="seagreen",
                                            "grid_2012"="seagreen2",
                                            "grid_2013"="steelblue",
                                            "grid_2014"='dodgerblue',
                                            "grid_2015" = "cyan3",
                                            'grid_2016' = 'blue',
                                            'grid_2017' = 'blue4',
                                            'grid_2018' = 'cadetblue',
                                            'grid_2019' = 'lightgreen',
                                            'grid_2020' = 'olivedrab',
                                            'grid_all' = 'steelblue3',
                                            "statn_2011"="maroon",
                                            "statn_2012"="deeppink4",
                                            "statn_2013"="deeppink",
                                            "statn_2014"='purple',
                                            "statn_2015" = "mediumorchid1",
                                            'statn_2016' = 'indianred',
                                            'statn_2017' = 'sienna',
                                            'statn_2018' = 'salmon2',
                                            'statn_2019' = 'mediumpurple1',
                                            'statn_2020' = 'violetred',
                                            'statn_all' = 'red')) +
  theme_bw(base_size=20)

@@

#plot annual cumulative Q vals for ensembles
plot_cumulq_yr_ <- function(calyear) {
  {flow_cumq %>%
    filter(year == calyear) %>%
    ggplot(aes(x = date,
               y = cumsum,
               color = cal_run)) +
    geom_line() +
scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            "grid_2011"="seagreen",
                                            "grid_2012"="seagreen2",
                                            "grid_2013"="steelblue",
                                            "grid_2014"='dodgerblue',
                                            "grid_2015" = "cyan3",
                                            'grid_2016' = 'blue',
                                            'grid_2017' = 'blue4',
                                            'grid_2018' = 'cadetblue',
                                            'grid_2019' = 'lightgreen',
                                            'grid_2020' = 'olivedrab',
                                            'grid_all' = 'steelblue3',
                                            "statn_2011"="maroon",
                                            "statn_2012"="deeppink4",
                                            "statn_2013"="deeppink",
                                            "statn_2014"='purple',
                                            "statn_2015" = "mediumorchid1",
                                            'statn_2016' = 'indianred',
                                            'statn_2017' = 'sienna',
                                            'statn_2018' = 'salmon2',
                                            'statn_2019' = 'mediumpurple1',
                                            'statn_2020' = 'violetred',
                                            'statn_all' = 'red')) +
    ggtitle(calyear) +
    theme_bw() +
    labs(y = 'Volume (m^3)')} %>%
    ggplotly()
}

@@

flow_kge_all <- flow %>%
  summarize(grid2011 = KGE(grid_2011, obs),
            grid2012 = KGE(grid_2012, obs),
            grid2013 = KGE(grid_2013, obs),
            grid2014 = KGE(grid_2014, obs),
            grid2015 = KGE(grid_2015, obs),
            grid2016 = KGE(grid_2016, obs),
            grid2017 = KGE(grid_2017, obs),
            grid2018 = KGE(grid_2018, obs),
            grid2019 = KGE(grid_2019, obs),
            grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs),
            statn2011 = KGE(statn_2011, obs),
            statn2012 = KGE(statn_2012, obs),
            statn2013 = KGE(statn_2013, obs),
            statn2014 = KGE(statn_2014, obs),
            statn2015 = KGE(statn_2015, obs),
            statn2016 = KGE(statn_2016, obs),
            statn2017 = KGE(statn_2017, obs),
            statn2018 = KGE(statn_2018, obs),
            statn2019 = KGE(statn_2019, obs),
            statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

@@

flow_year <- flow %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(
    grid2011 = KGE(grid_2011, obs),
            grid2012 = KGE(grid_2012, obs),
            grid2013 = KGE(grid_2013, obs),
            grid2014 = KGE(grid_2014, obs),
            grid2015 = KGE(grid_2015, obs),
            grid2016 = KGE(grid_2016, obs),
            grid2017 = KGE(grid_2017, obs),
            grid2018 = KGE(grid_2018, obs),
            grid2019 = KGE(grid_2019, obs),
            grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs, na.rm = T, method='2012'),
            statn2011 = KGE(statn_2011, obs),
            statn2012 = KGE(statn_2012, obs),
            statn2013 = KGE(statn_2013, obs),
            statn2014 = KGE(statn_2014, obs),
            statn2015 = KGE(statn_2015, obs),
            statn2016 = KGE(statn_2016, obs),
            statn2017 = KGE(statn_2017, obs),
            statn2018 = KGE(statn_2018, obs),
            statn2019 = KGE(statn_2019, obs),
            statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs, na.rm=T, method='2012')) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

@@

@@

flow_pbias_all <- flow %>%
  summarize(
    grid2011 = pbias(grid_2011, obs),
            grid2012 = pbias(grid_2012, obs),
            grid2013 = pbias(grid_2013, obs),
            grid2014 = pbias(grid_2014, obs),
            grid2015 = pbias(grid_2015, obs),
            grid2016 = pbias(grid_2016, obs),
            grid2017 = pbias(grid_2017, obs),
            grid2018 = pbias(grid_2018, obs),
            grid2019 = pbias(grid_2019, obs),
            grid2020 = pbias(grid_2020, obs),
            gridall = pbias(grid_all, obs),
            statn2011 = pbias(statn_2011, obs),
            statn2012 = pbias(statn_2012, obs),
            statn2013 = pbias(statn_2013, obs),
            statn2014 = pbias(statn_2014, obs),
            statn2015 = pbias(statn_2015, obs),
            statn2016 = pbias(statn_2016, obs),
            statn2017 = pbias(statn_2017, obs),
            statn2018 = pbias(statn_2018, obs),
            statn2019 = pbias(statn_2019, obs),
            statn2020 = pbias(statn_2020, obs),
            statnall = pbias(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

@@

flow_year <- flow %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(
    grid2011 = pbias(grid_2011, obs),
            grid2012 = pbias(grid_2012, obs),
            grid2013 = pbias(grid_2013, obs),
            grid2014 = pbias(grid_2014, obs),
            grid2015 = pbias(grid_2015, obs),
            grid2016 = pbias(grid_2016, obs),
            grid2017 = pbias(grid_2017, obs),
            grid2018 = pbias(grid_2018, obs),
            grid2019 = pbias(grid_2019, obs),
            grid2020 = pbias(grid_2020, obs),
            gridall = pbias(grid_all, obs),
            statn2011 = pbias(statn_2011, obs),
            statn2012 = pbias(statn_2012, obs),
            statn2013 = pbias(statn_2013, obs),
            statn2014 = pbias(statn_2014, obs),
            statn2015 = pbias(statn_2015, obs),
            statn2016 = pbias(statn_2016, obs),
            statn2017 = pbias(statn_2017, obs),
            statn2018 = pbias(statn_2018, obs),
            statn2019 = pbias(statn_2019, obs),
            statn2020 = pbias(statn_2020, obs),
            statnall = pbias(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

@@
